ODGI: understanding pangenome graphs

### 2021-11-08 manuscript/fig_extract_viz_draw_position_untangle.tex
spacy
update Fig4 with the 'final' WGG, with a bit more zoomed MHC locus; simplified the scripts

            \includegraphics[width=\linewidth, trim=0cm 18cm -20cm 0.5cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_gfa_og_mhc_og_O_og_lay_H1000w100_png_svg}

@@

        \textbf{(h)} Visualization of \textit{odgi untangle} output in the C4 pangenome graph: the plots show the copy number status of the sequences in the C4 region with respect to the grch38 reference sequence, making clear, for example, that in HG00438\#2, the \textit{C4B} gene is missing.

>>>>

            \includegraphics[width=\linewidth, trim=0cm 18cm -20cm 0.5cm]{fig/extract_viz_draw_position_untangle/chr6_pan_fa_a2fb268_4030258_6a1ecc2_smooth_mhc_H1000w120}

@@

        \textbf{(h)} Visualization of \textit{odgi untangle} output in the C4 pangenome graph: the plots show the copy number status of the sequences in the C4 region with respect to the grch38 reference sequence, making clear, for example, that in HG00438\#2, the \textit{C4B} gene is missing. \vspace{-1em}
